---
title: "Hassoun et al_ctDNA in Testicular Cancer Clinical Analysis"
output: html_notebook
---
library(swimplot)
library(coxphf)
library(grid)
library(gtable)
library(readr) 
library(mosaic)
library(dplyr) 
library(survival) 
library(survminer) 
library(ggplot2)
library(scales)
library(coxphf)
library(ggthemes)
library(tidyverse)
library(gtsummary)
library(flextable)
library(parameters)
library(car)
library(ComplexHeatmap)
library(tidyverse)
library(readxl)
library(survival)
library(janitor)
library(rms)
library(DT)

#ctDNA Detection rate by Stage and Window
```{r}
#Pre-Orchiectomy
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$preSx.ctDNA.anytime!="",]
circ_data$preSx.ctDNA.anytime <- factor(circ_data$preSx.ctDNA.anytime, levels=c("NEGATIVE","POSITIVE"))
circ_data$Stage <- factor(circ_data$Stage, levels=c("I","II","III"))
circ_data <- subset(circ_data, preSx.ctDNA.anytime %in% c("NEGATIVE", "POSITIVE"))
positive_counts_by_stage <- aggregate(circ_data$preSx.ctDNA.anytime == "POSITIVE", by=list(circ_data$Stage), FUN=sum)
total_counts_by_stage <- aggregate(circ_data$preSx.ctDNA.anytime, by=list(circ_data$Stage), FUN=length)
combined_data <- data.frame(
  Stage = total_counts_by_stage$Group.1,
  Total_Count = total_counts_by_stage$x,
  Positive_Count = positive_counts_by_stage$x,
  Rate = (positive_counts_by_stage$x / total_counts_by_stage$x) * 100  # Convert to percentage
)
combined_data$Rate <- sprintf("%.2f%%", combined_data$Rate)
overall_total_count <- nrow(circ_data)
overall_positive_count <- nrow(circ_data[circ_data$preSx.ctDNA.anytime == "POSITIVE",])
overall_positivity_rate <- (overall_positive_count / overall_total_count) * 100  # Convert to percentage
overall_row <- data.frame(
  Stage = "Overall",
  Total_Count = overall_total_count,
  Positive_Count = overall_positive_count,
  Rate = sprintf("%.2f%%", overall_positivity_rate)
)
combined_data <- rbind(combined_data, overall_row)
print(combined_data)

#MRD Window
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$ctDNA.MRD.Window!="",]
circ_data$ctDNA.MRD.Window <- factor(circ_data$ctDNA.MRD.Window, levels=c("NEGATIVE","POSITIVE"))
circ_data$Stage <- factor(circ_data$Stage, levels=c("I","II","III"))
circ_data <- subset(circ_data, ctDNA.MRD.Window %in% c("NEGATIVE", "POSITIVE"))
positive_counts_by_stage <- aggregate(circ_data$ctDNA.MRD.Window == "POSITIVE", by=list(circ_data$Stage), FUN=sum)
total_counts_by_stage <- aggregate(circ_data$ctDNA.MRD.Window, by=list(circ_data$Stage), FUN=length)
combined_data <- data.frame(
  Stage = total_counts_by_stage$Group.1,
  Total_Count = total_counts_by_stage$x,
  Positive_Count = positive_counts_by_stage$x,
  Rate = (positive_counts_by_stage$x / total_counts_by_stage$x) * 100  # Convert to percentage
)
combined_data$Rate <- sprintf("%.2f%%", combined_data$Rate)
overall_total_count <- nrow(circ_data)
overall_positive_count <- nrow(circ_data[circ_data$ctDNA.MRD.Window == "POSITIVE",])
overall_positivity_rate <- (overall_positive_count / overall_total_count) * 100  # Convert to percentage
overall_row <- data.frame(
  Stage = "Overall",
  Total_Count = overall_total_count,
  Positive_Count = overall_positive_count,
  Rate = sprintf("%.2f%%", overall_positivity_rate)
)
combined_data <- rbind(combined_data, overall_row)
print(combined_data)

#Surveillance Window
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$ctDNA.surveillance!="",]
circ_data$ctDNA.MRD.Window <- factor(circ_data$ctDNA.surveillance, levels=c("NEGATIVE","POSITIVE"))
circ_data$Stage <- factor(circ_data$Stage, levels=c("I","II","III"))
circ_data <- subset(circ_data, ctDNA.surveillance %in% c("NEGATIVE", "POSITIVE"))
positive_counts_by_stage <- aggregate(circ_data$ctDNA.surveillance == "POSITIVE", by=list(circ_data$Stage), FUN=sum)
total_counts_by_stage <- aggregate(circ_data$ctDNA.surveillance, by=list(circ_data$Stage), FUN=length)
combined_data <- data.frame(
  Stage = total_counts_by_stage$Group.1,
  Total_Count = total_counts_by_stage$x,
  Positive_Count = positive_counts_by_stage$x,
  Rate = (positive_counts_by_stage$x / total_counts_by_stage$x) * 100  # Convert to percentage
)
combined_data$Rate <- sprintf("%.2f%%", combined_data$Rate)
overall_total_count <- nrow(circ_data)
overall_positive_count <- nrow(circ_data[circ_data$ctDNA.surveillance == "POSITIVE",])
overall_positivity_rate <- (overall_positive_count / overall_total_count) * 100  # Convert to percentage
overall_row <- data.frame(
  Stage = "Overall",
  Total_Count = overall_total_count,
  Positive_Count = overall_positive_count,
  Rate = sprintf("%.2f%%", overall_positivity_rate)
)
combined_data <- rbind(combined_data, overall_row)
print(combined_data)

#Anytime post-surgery
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$postSx.ctDNA.anytime!="",]
circ_data$postSx.ctDNA.anytime <- factor(circ_data$postSx.ctDNA.anytime, levels=c("NEGATIVE","POSITIVE"))
circ_data$Stage <- factor(circ_data$Stage, levels=c("I","II","III"))
circ_data <- subset(circ_data, postSx.ctDNA.anytime %in% c("NEGATIVE", "POSITIVE"))
positive_counts_by_stage <- aggregate(circ_data$postSx.ctDNA.anytime == "POSITIVE", by=list(circ_data$Stage), FUN=sum)
total_counts_by_stage <- aggregate(circ_data$postSx.ctDNA.anytime, by=list(circ_data$Stage), FUN=length)
combined_data <- data.frame(
  Stage = total_counts_by_stage$Group.1,
  Total_Count = total_counts_by_stage$x,
  Positive_Count = positive_counts_by_stage$x,
  Rate = (positive_counts_by_stage$x / total_counts_by_stage$x) * 100  # Convert to percentage
)
combined_data$Rate <- sprintf("%.2f%%", combined_data$Rate)
overall_total_count <- nrow(circ_data)
overall_positive_count <- nrow(circ_data[circ_data$postSx.ctDNA.anytime == "POSITIVE",])
overall_positivity_rate <- (overall_positive_count / overall_total_count) * 100  # Convert to percentage
overall_row <- data.frame(
  Stage = "Overall",
  Total_Count = overall_total_count,
  Positive_Count = overall_positive_count,
  Rate = sprintf("%.2f%%", overall_positivity_rate)
)
combined_data <- rbind(combined_data, overall_row)
print(combined_data)
```

#Demographics Table
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]

circ_data_subset <- circ_data %>%
  select(
    Age,
    pT,
    Stage,
    Histology,
    Treatment,
    RPLND.Pathology,
    preSx.markers.anytime,
    Markers.postSx.anytime,
    PFS.Event,
    OS.Event,
    OS.months) %>%
  mutate(
    Age = as.numeric(Age),
    pT = factor(pT, levels = c("0","1", "2", "3", "X"), labels = c("pT0","pT1", "pT2", "pT3","pTX")),
    Stage = factor(Stage, levels = c("I", "II", "III")),
    Histology = factor(Histology, levels = c("Non seminoma", "Seminoma")),
    Treatment = factor(Treatment, levels = c("Surveillance", "Chemotherapy", "RPLND", "RPLND, Chemotherapy")),
    RPLND.Pathology = factor(RPLND.Pathology, levels = c("Negative", "Germ Cell/Teratoma")),
    preSx.markers.anytime = factor(preSx.markers.anytime, levels = c("NEGATIVE", "POSITIVE"), labels = c("Normal", "Elevated")),
    Markers.postSx.anytime = factor(Markers.postSx.anytime, levels = c("NEGATIVE", "POSITIVE"), labels = c("Normal", "Elevated")),
    PFS.Event = factor(PFS.Event, levels = c("FALSE", "TRUE"), labels = c("No Event", "Event")),
    OS.Event = factor(OS.Event, levels = c("FALSE", "TRUE"), labels = c("Alive", "Deceased")),
    OS.months = as.numeric(OS.months))
table1 <- circ_data_subset %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{median} ({min} - {max})",
      all_categorical() ~ "{n} ({p}%)"),
    label = list(
      Age ~ "Age",
      pT ~ "Pathological T Stage",
      Stage ~ "Overall Stage",
      Histology ~ "Histology",
      Treatment ~ "Post-surgery treatment",
      RPLND.Pathology ~ "RPLND Pathology",
      preSx.markers.anytime ~ "Serum Markers pre-op",
      Markers.postSx.anytime ~ "Serum Markers anytime post-op",
      PFS.Event ~ "Event During Follow-up",
      OS.Event ~ "Vital Status",
      OS.months ~ "Total Follow up (months)"),) %>%
  bold_labels()
table1
fit1 <- as_flex_table(
  table1,
  include = everything(),
  return_calls = FALSE,
  strip_md_bold = TRUE)
fit1
save_as_docx(fit1, path= "~/Downloads/table1.docx")
```


#Heatmap with Clinical & Genomics Factors
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data %>% arrange(Stage)
circ_datadf <- as.data.frame(circ_data)

ha <- HeatmapAnnotation(
  Stage = circ_data$Stage,
  Histology = circ_data$Histology,
  pT = circ_data$pT,
  Treatment = circ_data$Treatment,
  Platinum.Response = circ_data$Platinum.Response,
  PFS.Event = circ_data$PFS.Event,
  preSx.markers.anytime = circ_data$preSx.markers.anytime,
  Markers.MRD.Window = circ_data$Markers.MRD.Window,
  Markers.Surveillance = circ_data$Markers.Surveillance,
  Markers.post.ACT = circ_data$Markers.post.ACT,
  Markers.post.RPLND = circ_data$Markers.post.RPLND,
  Markers.postSx.anytime = circ_data$Markers.postSx.anytime,
  Markers.anytime = circ_data$Markers.anytime,
  preSx.ctDNA.anytime = circ_data$preSx.ctDNA.anytime,
  ctDNA.MRD.Window = circ_data$ctDNA.MRD.Window,
  ctDNA.surveillance = circ_data$ctDNA.surveillance,
  ctDNA.post.ACT = circ_data$ctDNA.post.ACT,
  ctDNA.post.RPLND = circ_data$ctDNA.post.RPLND,
  postSx.ctDNA.anytime = circ_data$postSx.ctDNA.anytime,
  ctDNA.anytime = circ_data$ctDNA.anytime,
  
  col = list(Stage = c("I" = "seagreen1", "II" = "orange", "III" = "purple"),
    Histology = c("Non seminoma" = "goldenrod" , "Seminoma" = "blue4"),
    pT = c("0" = "coral","1" = "coral", "2" ="darkgreen", "3" = "yellow3", "X" = "gray"),
    Treatment = c("Surveillance" = "lightblue", "Chemotherapy" = "orange2", "RPLND" ="khaki", "RPLND, Chemotherapy" = "brown2"),
    Platinum.Response = c("SD/PD" = "red3", "PR/CR" ="blue"),
    PFS.Event = c("TRUE" = "red3", "FALSE" ="blue"),
    preSx.markers.anytime = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    Markers.MRD.Window = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    Markers.Surveillance = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    Markers.post.ACT = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    Markers.post.RPLND = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    Markers.postSx.anytime = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    Markers.anytime = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    preSx.ctDNA.anytime = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    ctDNA.MRD.Window = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    ctDNA.surveillance = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    ctDNA.post.ACT = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    ctDNA.post.RPLND = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    postSx.ctDNA.anytime = c("POSITIVE" = "red3", "NEGATIVE" ="blue"),
    ctDNA.anytime = c("POSITIVE" = "red3", "NEGATIVE" ="blue")
)
)
ht <- Heatmap(matrix(nrow = 0, ncol = length(circ_data$Stage)),show_row_names = FALSE,cluster_rows = F,cluster_columns = FALSE, top_annotation = ha)
pdf("heatmap.pdf",width = 7, height = 7)
draw(ht, annotation_legend_side = "bottom")
dev.off()
```


#Overview plot
```{r}
library(swimplot)
library(ggplot2)
library(grid)
library(gtable)

#Overview plot
rm(list=ls())
setwd("~/Downloads")
clinstage<- read.csv("CLIA Testicular_OP.csv")
clinstage_df<- as.data.frame(clinstage)

oplot_stratify <-swimmer_plot(df=clinstage_df,
                              id='PatientName',
                              end='fu.diff.months',
                              #name_fill='Arm',
                              col="gray",
                              alpha=0.75,
                              width=.01,
                              base_size = 14,
                              )
oplot_stratify <- oplot_stratify + theme(panel.border = element_blank())
oplot_stratify <- oplot_stratify + scale_y_continuous(breaks = seq(0, 108, by = 6))
oplot_stratify <- oplot_stratify + labs(x ="Patients" , y="Months from Orchiectomy")
oplot_stratify

#plot events
oplot_ev3 <- oplot_stratify + swimmer_points(df_points=clinstage_df,
                                             id='PatientName',
                                             time='date.diff.months',
                                             name_shape ='Event_type',
                                             name_col = 'Event',
                                             size=3.5,fill='black',
                                             #col='darkgreen'
)
oplot_ev3

#Shape customization to Event_type

oplot_ev3.1 <- oplot_ev3 + ggplot2::scale_shape_manual(name="Event_type",values=c(1,16,1,16,6,18,18,4),breaks=c('ctDNA_neg','ctDNA_pos','markers_neg','markers_pos','Imaging','Surgery','RPLND', 'Death'))

oplot_ev3.1

#plot treatment
oplot_ev4 <- oplot_ev3.1 + swimmer_lines(df_lines=clinstage_df,
                                         id='PatientName',
                                         start='Tx_start.months',
                                         end='Tx_end.months',
                                         name_col='Tx_type',
                                         size=3.5,
                                         name_alpha = 1.0)
oplot_ev4 <- oplot_ev4 + guides(linetype = guide_legend(override.aes = list(size = 5, color = "black")))
oplot_ev4  


#colour customization
oplot_ev4.2 <- oplot_ev4 + ggplot2::scale_color_manual(name="Event",values=c( "lightblue", "black", "black", "green", "red", "orange", "grey", "purple", "blue"))
oplot_ev4.2
```


#Overview plot Stratified by Stage
```{r}
library(swimplot)
library(ggplot2)
library(grid)
library(gtable)

#Overview plot
rm(list=ls())
setwd("~/Downloads")
clinstage<- read.csv("CLIA Testicular_OP.csv")
clinstage_df<- as.data.frame(clinstage)

oplot_stratify <-swimmer_plot(df=clinstage_df,
                              id='PatientName',
                              end='fu.diff.months',
                              #name_fill='Arm',
                              col="gray",
                              alpha=0.75,
                              width=.01,
                              base_size = 14,
                              stratify= c('Stage'))
oplot_stratify <- oplot_stratify + theme(panel.border = element_blank())
oplot_stratify <- oplot_stratify + scale_y_continuous(breaks = seq(0, 108, by = 6))
oplot_stratify <- oplot_stratify + labs(x ="Patients" , y="Months from Orchiectomy")
oplot_stratify

#plot events
oplot_ev3 <- oplot_stratify + swimmer_points(df_points=clinstage_df,
                                             id='PatientName',
                                             time='date.diff.months',
                                             name_shape ='Event_type',
                                             name_col = 'Event',
                                             size=3.5,fill='black',
                                             #col='darkgreen'
)
oplot_ev3

#Shape customization to Event_type

oplot_ev3.1 <- oplot_ev3 + ggplot2::scale_shape_manual(name="Event_type",values=c(1,16,1,16,6,18,18,4),breaks=c('ctDNA_neg','ctDNA_pos','markers_neg','markers_pos','Imaging','Surgery','RPLND', 'Death'))

oplot_ev3.1

#plot treatment
oplot_ev4 <- oplot_ev3.1 + swimmer_lines(df_lines=clinstage_df,
                                         id='PatientName',
                                         start='Tx_start.months',
                                         end='Tx_end.months',
                                         name_col='Tx_type',
                                         size=3.5,
                                         name_alpha = 1.0)
oplot_ev4 <- oplot_ev4 + guides(linetype = guide_legend(override.aes = list(size = 5, color = "black")))
oplot_ev4  


#colour customization
oplot_ev4.2 <- oplot_ev4 + ggplot2::scale_color_manual(name="Event",values=c( "lightblue", "black", "black", "green", "red", "orange", "grey", "purple", "blue"))
oplot_ev4.2
```


#Sankey Plots for all pts with post-orchiectomy timepoint available
```{r}
##To run this commands, please visit: https://sankeymatic.com/build/
#No pre-orch [20] MRD positive #E67272
#No pre-orch [12] MRD negative #87EA86
#No pre-orch [27] no MRD timepoint #808080
#Pre-orch Positive [1] MRD positive #E67272
#Pre-orch Positive [8] MRD negative #87EA86
#Pre-orch Positive [5] no MRD timepoint #808080
#Pre-orch Negative [1] MRD negative #87EA86

#MRD positive [7] Surveillance positive #E67272
#MRD positive [7] Surveillance negative #87EA86
#MRD positive [7] no Surveillance timepoint #80808
#MRD negative [1] Surveillance positive #E67272
#MRD negative [18] Surveillance negative #87EA86
#MRD negative [2] no Surveillance timepoint #80808
#no MRD timepoint [5] Surveillance positive #E67272
#no MRD timepoint [13] Surveillance negative #87EA86
#no MRD timepoint [14] no Surveillance timepoint #808080

#Surveillance positive [13] Event #E67272
#Surveillance positive [0] No Event #87EA86
#Surveillance negative [5] Event #E67272
#Surveillance negative [33] No Event #87EA86
#no Surveillance timepoint [17] Event #E67272
#no Surveillance timepoint [6] No Event #87EA86
```


#EFS by ctDNA at the MRD Window
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$ctDNA.MRD.Window!="",]
circ_datadf <- as.data.frame(circ_data)

survfit(Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)~ctDNA.MRD.Window, data = circ_data)
event_summary <- circ_data %>%
  group_by(ctDNA.MRD.Window) %>%
  summarise(
    Total = n(),
    Events = sum(PFS.Event),
    Fraction = Events / n(),
    Percentage = (Events / n()) * 100
  )
print(event_summary)
surv_object <-Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)
KM_curve <- survfit(surv_object ~ ctDNA.MRD.Window, data = circ_data,conf.int=0.95,conf.type="log-log") 
ggsurvplot(KM_curve, data = circ_data, pval = FALSE, conf.int = FALSE, risk.table = TRUE, break.time.by=6, palette=c("blue","red"), title="EFS - ctDNA MRD window", ylab= "Event-Free Survival", xlab="Months from Orchiectomy", legend.labs=c("ctDNA Negative", "ctDNA Positive"), legend.title="")
summary(KM_curve, times= c(12, 24))
circ_data$ctDNA.MRD.Window <- factor(circ_data$ctDNA.MRD.Window, levels=c("NEGATIVE","POSITIVE"))
circ_data$Disease.Type <- factor(circ_data$Disease.Type, levels = c("Primary", "Metastatic"))
circ_data$Histology <- factor(circ_data$Histology, levels = c("Non seminoma", "Seminoma"), labels = c("Non seminoma", "Seminoma"))
cox_fit <- coxph(surv_object ~ ctDNA.MRD.Window + Disease.Type + Histology, data=circ_data) 
ggforest(cox_fit,data = circ_data) 
summary(cox_fit)
```




#EFS by STMs at the MRD Window
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$ctDNA.MRD.Window!="",]
circ_data <- circ_data[circ_data$Markers.MRD.Window!="",]
circ_datadf <- as.data.frame(circ_data)

survfit(Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)~Markers.MRD.Window, data = circ_data)
event_summary <- circ_data %>%
  group_by(Markers.MRD.Window) %>%
  summarise(
    Total = n(),
    Events = sum(PFS.Event),
    Fraction = Events / n(),
    Percentage = (Events / n()) * 100
  )
print(event_summary)
surv_object <-Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)
KM_curve <- survfit(surv_object ~ Markers.MRD.Window, data = circ_data,conf.int=0.95,conf.type="log-log") 
ggsurvplot(KM_curve, data = circ_data, pval = FALSE, conf.int = FALSE, risk.table = TRUE, break.time.by=6, palette=c("blue","red"), title="EFS - STM at MRD window", ylab= "Event-Free Survival", xlab="Months from Orchiectomy", legend.labs=c("Normal", "Elevated"), legend.title="")
summary(KM_curve, times= c(12))
circ_data$Markers.MRD.Window <- factor(circ_data$Markers.MRD.Window, levels=c("NEGATIVE","POSITIVE"))
circ_data$Disease.Type <- factor(circ_data$Disease.Type, levels = c("Primary", "Metastatic"))
circ_data$Histology <- factor(circ_data$Histology, levels = c("Non seminoma", "Seminoma"), labels = c("Non seminoma", "Seminoma"))
cox_fit <- coxph(surv_object ~ Markers.MRD.Window + Disease.Type + Histology, data=circ_data) 
ggforest(cox_fit,data = circ_data) 
summary(cox_fit)
```




#Multivariate regression model for EFS at the MRD Window
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$ctDNA.MRD.Window!="",]
circ_datadf <- as.data.frame(circ_data)

circ_datadf$Disease.Type <- factor(circ_datadf$Disease.Type, levels = c("Primary", "Metastatic"), labels = c("I/II", "III"))
circ_datadf$Histology <- factor(circ_datadf$Histology, levels = c("Non seminoma", "Seminoma"), labels = c("Non seminoma", "Seminoma"))
circ_datadf$Markers.MRD.Window <- factor(circ_datadf$Markers.MRD.Window, levels=c("NEGATIVE","POSITIVE"), labels = c("Normal", "Elevated"))
circ_datadf$ctDNA.MRD.Window <- factor(circ_datadf$ctDNA.MRD.Window, levels=c("NEGATIVE","POSITIVE"), labels = c("Negative", "Positive"))
surv_object<-Surv(time = circ_datadf$PFS.months, event = circ_datadf$PFS.Event) 
cox_fit <- coxph(surv_object ~ Age + Disease.Type + Histology + Markers.MRD.Window + ctDNA.MRD.Window, data=circ_datadf) 
ggforest(cox_fit, data = circ_datadf, main = "Multivariate Regression Model for EFS", refLabel = "Reference Group")
test.ph <- cox.zph(cox_fit)
```

#EFS by ctDNA at the Surveillance Window
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$ctDNA.surveillance!="",]
circ_datadf <- as.data.frame(circ_data)

survfit(Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)~ctDNA.surveillance, data = circ_data)
event_summary <- circ_data %>%
  group_by(ctDNA.surveillance) %>%
  summarise(
    Total = n(),
    Events = sum(PFS.Event),
    Fraction = Events / n(),
    Percentage = (Events / n()) * 100
  )
print(event_summary)
surv_object <-Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)
KM_curve <- survfit(surv_object ~ ctDNA.surveillance, data = circ_data,conf.int=0.95,conf.type="log-log") 
ggsurvplot(KM_curve, data = circ_data, pval = FALSE, conf.int = FALSE, risk.table = TRUE, break.time.by=6, palette=c("blue","red"), title="EFS - ctDNA Surveillance window", ylab= "Event-Free Survival", xlab="Months from Orchiectomy", legend.labs=c("ctDNA Negative", "ctDNA Positive"), legend.title="")
summary(KM_curve, times= c(12))
circ_data$ctDNA.surveillance <- factor(circ_data$ctDNA.surveillance, levels=c("NEGATIVE","POSITIVE"))
circ_data$Disease.Type <- factor(circ_data$Disease.Type, levels = c("Primary", "Metastatic"))
circ_data$Histology <- factor(circ_data$Histology, levels = c("Non seminoma", "Seminoma"), labels = c("Non seminoma", "Seminoma"))
cox_fit <- coxph(surv_object ~ ctDNA.surveillance + Disease.Type + Histology, data=circ_data)
ggforest(cox_fit,data = circ_data) 
summary(cox_fit)
```




#EFS by Serum Markers at the Surveillance Window
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$Markers.Surveillance!="",]
circ_datadf <- as.data.frame(circ_data)

survfit(Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)~Markers.Surveillance, data = circ_data)
event_summary <- circ_data %>%
  group_by(Markers.Surveillance) %>%
  summarise(
    Total = n(),
    Events = sum(PFS.Event),
    Fraction = Events / n(),
    Percentage = (Events / n()) * 100
  )
print(event_summary)
surv_object <-Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)
KM_curve <- survfit(surv_object ~ Markers.Surveillance, data = circ_data,conf.int=0.95,conf.type="log-log") 
ggsurvplot(KM_curve, data = circ_data, pval = FALSE, conf.int = FALSE, risk.table = TRUE, break.time.by=6, palette=c("blue","red"), title="EFS - Serum Markers Surveillance window", ylab= "Event-Free Survival", xlab="Months from Orchiectomy", legend.labs=c("Normal", "Elevated"), legend.title="")
summary(KM_curve, times= c(12))
circ_data$Markers.Surveillance <- factor(circ_data$Markers.Surveillance, levels=c("NEGATIVE","POSITIVE"))
circ_data$Disease.Type <- factor(circ_data$Disease.Type, levels = c("Primary", "Metastatic"))
circ_data$Histology <- factor(circ_data$Histology, levels = c("Non seminoma", "Seminoma"), labels = c("Non seminoma", "Seminoma"))
cox_fit <- coxph(surv_object ~ Markers.Surveillance + Disease.Type + Histology, data=circ_data)
ggforest(cox_fit,data = circ_data) 
summary(cox_fit)
```




#EFS by ctDNA at post-RPLND - Stage II
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$RPLND==TRUE,]
circ_data <- circ_data[circ_data$Stage=="II",]
circ_data <- circ_data[circ_data$ctDNA.post.RPLND!="",]
circ_datadf <- as.data.frame(circ_data)

survfit(Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)~ctDNA.post.RPLND, data = circ_data)
event_summary <- circ_data %>%
  group_by(ctDNA.post.RPLND) %>%
  summarise(
    Total = n(),
    Events = sum(PFS.Event),
    Fraction = Events / n(),
    Percentage = (Events / n()) * 100
  )
print(event_summary)
surv_object <-Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)
KM_curve <- survfit(surv_object ~ ctDNA.post.RPLND, data = circ_data,conf.int=0.95,conf.type="log-log") 
ggsurvplot(KM_curve, data = circ_data, pval = TRUE, conf.int = FALSE, risk.table = TRUE, break.time.by=3, palette=c("blue","red"), title="EFS - ctDNA post-RPLND - Stage II", ylab= "Event-Free Survival", xlab="Months from Orchiectomy", legend.labs=c("ctDNA Negative", "ctDNA Positive"), legend.title="")
summary(KM_curve, times= c(0, 12))
circ_data$ctDNA.post.RPLND <- factor(circ_data$ctDNA.post.RPLND, levels=c("NEGATIVE","POSITIVE"))
cox_fit <- coxphf(surv_object ~ ctDNA.post.RPLND, data=circ_data) 
summary(cox_fit)
```




#EFS by ctDNA at post-ACT - Stage II/III
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$ACT==TRUE,]
circ_data <- circ_data[circ_data$Stage!="I",]
circ_data <- circ_data[circ_data$ctDNA.surveillance!="",]
circ_datadf <- as.data.frame(circ_data)

survfit(Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)~ctDNA.surveillance, data = circ_data)
event_summary <- circ_data %>%
  group_by(ctDNA.surveillance) %>%
  summarise(
    Total = n(),
    Events = sum(PFS.Event),
    Fraction = Events / n(),
    Percentage = (Events / n()) * 100
  )
print(event_summary)
surv_object <-Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)
KM_curve <- survfit(surv_object ~ ctDNA.surveillance, data = circ_data,conf.int=0.95,conf.type="log-log") 
ggsurvplot(KM_curve, data = circ_data, pval = FALSE, conf.int = FALSE, risk.table = TRUE, break.time.by=3, palette=c("blue","red"), title="EFS - ctDNA post-ACT - Stage II/III", ylab= "Event-Free Survival", xlab="Months from Orchiectomy", legend.labs=c("ctDNA Negative", "ctDNA Positive"), legend.title="")
summary(KM_curve, times= c(12, 24))
circ_data$ctDNA.surveillance <- factor(circ_data$ctDNA.surveillance, levels=c("NEGATIVE","POSITIVE"))
cox_fit <- coxph(surv_object ~ ctDNA.surveillance, data=circ_data) 
ggforest(cox_fit,data = circ_data) 
summary(cox_fit)
cox_fit_summary <- summary(cox_fit)

# Extract values for HR, 95% CI, and p-value
HR <- cox_fit_summary$coefficients[2]
lower_CI <- cox_fit_summary$conf.int[3]
upper_CI <- cox_fit_summary$conf.int[4]
p_value <- cox_fit_summary$coefficients[5]
label_text <- paste0("HR = ", round(HR, 2), " (", round(lower_CI, 2), "-", round(upper_CI, 2), "); p = ", round(p_value, 3))
print(label_text)
```





#EFS by STMs at post-ACT - Stage II/III
```{r}
rm(list=ls())
setwd("~/Downloads")
circ_data <- read.csv("CLIA Testicular_GL.csv")
circ_data <- circ_data[circ_data$ctDNA.available==TRUE,]
circ_data <- circ_data[circ_data$ACT==TRUE,]
circ_data <- circ_data[circ_data$Stage!="I",]
circ_data <- circ_data[circ_data$Markers.Surveillance!="",]
circ_datadf <- as.data.frame(circ_data)

survfit(Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)~Markers.Surveillance, data = circ_data)
event_summary <- circ_data %>%
  group_by(Markers.Surveillance) %>%
  summarise(
    Total = n(),
    Events = sum(PFS.Event),
    Fraction = Events / n(),
    Percentage = (Events / n()) * 100
  )
print(event_summary)
surv_object <-Surv(time = circ_data$PFS.months, event = circ_data$PFS.Event)
KM_curve <- survfit(surv_object ~ Markers.Surveillance, data = circ_data,conf.int=0.95,conf.type="log-log") 
ggsurvplot(KM_curve, data = circ_data, pval = FALSE, conf.int = FALSE, risk.table = TRUE, break.time.by=6, palette=c("blue","red"), title="EFS - STMs post-ACT - Stage II/III", ylab= "Event-Free Survival", xlab="Months from Orchiectomy", legend.labs=c("Normal", "Elevated"), legend.title="")
summary(KM_curve, times= c(12, 24))
circ_data$Markers.Surveillance <- factor(circ_data$Markers.Surveillance, levels=c("NEGATIVE","POSITIVE"))
cox_fit <- coxph(surv_object ~ Markers.Surveillance, data=circ_data) 
ggforest(cox_fit,data = circ_data) 
summary(cox_fit)
cox_fit_summary <- summary(cox_fit)

# Extract values for HR, 95% CI, and p-value
HR <- cox_fit_summary$coefficients[2]
lower_CI <- cox_fit_summary$conf.int[3]
upper_CI <- cox_fit_summary$conf.int[4]
p_value <- cox_fit_summary$coefficients[5]
label_text <- paste0("HR = ", round(HR, 2), " (", round(lower_CI, 2), "-", round(upper_CI, 2), "); p = ", round(p_value, 3))
print(label_text)
```

